Motion Planning and Robust Decentralized Fault-Tolerant Tracking Control of Hybrid UAVs and Biped Robots Team System for Search and Rescue Usage

### 2022-12-08 paper/paper.tex
- Robot, noFTC, simulation+paper, done - SearchTaskThreeTeam, robot reference ok

In order to show the effect of active FTC based on the proposed embed smoothing model method, a traditional PID computed torque controller without FTC is used for comparison \cite{7456706}. In order to only focus on the effect of FTC, the method in \cite{7456706} was revised to oberserver based, that is, the control law become $u(t)= M(r(t))(\ddot{r}(t) + u_{fb}(t)) + H(r(t),\dot{r}(t))$ where $u_{fb}(t) = [K_I, K_P, K_D][\int_{0}^{t}\hat{e}^T(\tau)d\tau, \hat{e}^T(t), \dot{\hat{e}}^T(t)]^T$. The results are shown in Fig. \ref{fig:uav, state, noFTC} for UAV and Fig. \ref{fig:robot, state, noFTC} for robot. From Fig. \ref{fig:uav, state, noFTC} and Fig. \ref{fig:robot, state, noFTC}, it can be clearly seen that the influence of the acuator fault $f_1$ on the tracking error is revealed. The value of sensor fault $f_2$ is relatively insignificant because it is much smaller than that of acuator fault by our simulation setting but $x_4,x_5,x_6$ can still see the ups and downs with a period of 10 seconds. Although still stable, its tracking performance has dropped significantly compared to Fig. \ref{fig:UAV, state}.
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.57]{fig/uav (1) noFTC.png}\caption{The trajectories of reference, state and estimated state of the UAV $\alpha_{1,1}$ by traditional PID computed torque controller without FTC \cite{7456706}}%
    \label{fig:uav, state, noFTC}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.57]{fig/uav (1) noFTC.png}\caption{The trajectories of reference, state and estimated state of the robot $\alpha_{1,2}$ by traditional PID computed torque controller without FTC \cite{7456706}}%
    \label{fig:robot, state, noFTC}
\end{figure}

>>>>

In order to show the effect of active FTC based on the proposed embed smoothing model method, a traditional PID computed torque controller without FTC is used for comparison \cite{7456706}. In order to only focus on the effect of FTC, the method in \cite{7456706} was revised to oberserver based, that is, the control law become $u(t)= M(r(t))(\ddot{r}(t) + u_{fb}(t)) + H(r(t),\dot{r}(t))$ where $u_{fb}(t) = [K_I, K_P, K_D][\int_{0}^{t}\hat{e}^T(\tau)d\tau, \hat{e}^T(t), \dot{\hat{e}}^T(t)]^T$. The results are shown in Fig. \ref{fig:uav, state, noFTC} for UAV and Fig. \ref{fig:robot, state, noFTC} for robot. From Fig. \ref{fig:uav, state, noFTC} and Fig. \ref{fig:robot, state, noFTC}, it can be clearly seen that the influence of the acuator fault $f_1$ on the tracking error is revealed. The influence of the sensor fault $f_2$ is relatively insignificant because its value is much smaller than $f_1$ by our simulation setting. However, the fluctuation of $f_2$ with a period of 10 seconds (corresponding to the period of the smoothed square wave) can still be seen from the UAV attitude state variables $x_4,x_5,x_6$ in Fig. \ref{fig:uav, state, noFTC} and the robot joint state variables $x_5,x_6,x_{11},x_{12}$ in Fig. \ref{fig:robot, state, noFTC}. Although it still stable, the tracking performance has dropped significantly compared to Fig. \ref{fig:UAV, state} and \ref{fig:robot, state}, respectively.
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.57]{fig/uav (1) noFTC.png}\caption{The trajectories of reference, state and estimated state of the UAV $\alpha_{1,1}$ by traditional PID computed torque controller without FTC \cite{7456706}}%
    \label{fig:uav, state, noFTC}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.57]{fig/robot (1) noFTC.png}\caption{The trajectories of reference, state and estimated state of the robot $\alpha_{1,2}$ by traditional PID computed torque controller without FTC \cite{7456706}}%
    \label{fig:robot, state, noFTC}
\end{figure}
